On the discovery and origin of $r$-process stars in the Milky Way

### 2018-02-07 article/ms.tex
minor

	The LAMOST survey is a low resolution ($R\approx1800$) optical survey that took spectra of stars between 3650-9000 \AA. The second data release from the LAMOST telescope catalogued $\approx$ 2.2 million spectra (low resolution) of stars in the northern sky. Of these 2.2 million, 454,180 giants were fit against a normalised spectra from a sample of 9952 giants \citep{AnnaHo2017}, and from this it became possible to analyse which giants showed an abundance or depletion of particular heavy elements. A machine learning code \textit{The Cannon} was used to fit a predictive model using 9952 LAMOST giant stars that were also found in the higher resolution ($R\approx22500$) APOGEE survey. The labels \textit{The Cannon} predicted were $T_{\rm{eff}}$, $\rm{log_{10}[g]}$, $\rm{[Fe/H]}$, and $\rm{[\alpha/Fe]}$. Normalised spectra was then fit to 454,180 giants from the LAMOST survey and was restricted to between 3905\,\AA\ and 9000\,\AA. For reference, typical uncertainties for these labels are $70\rm{K}$ for $T_{\rm{eff}}$, $0.1$ in $\rm{log_{10}[g]}$, 0.1 in $\rm{[Fe/H]}$, and 0.04 in $\rm{[\alpha/H]}$.

	We selected potential candidate stars with an over-abundance of Europium by searching for deviations from the normalized spectra supplied by \textit{The Cannon}. A negative deviation implies an enhancement in a particular element while a positive deviation implies a depletion (compared to what the data-driven model predicted).

>>>>

	The LAMOST survey is a low resolution optical spectroscopic survey ($R\approx1800$; 3650-9000\,\AA). The second data release from  LAMOST \citep{lamost} contains about 2.2 million stellar spectra in the northern sky. Of these 2.2 million, 454,180 were identified as giant stars through a data-driven analysis known as \textit{The Cannon}. An overlap sample of 9,952 giant stars common to LAMOST and the higher-resolution ($R\approx22500$) APOGEE survey \citep{apogee} were used as a training set.
	The stellar labels used by \textit{The Cannon} included $T_{\rm{eff}}$, $\log{g}$, $\rm{[Fe/H]}$, and $\rm{[\alpha/Fe]}$. For reference, typical uncertainties for these labels are about $70\rm{K}$ for $T_{\rm{eff}}$, $0.1$ in $\rm{log_{10}{g}}$, 0.1\,dex in $\rm{[Fe/H]}$, and 0.04\,dex in $\rm{[\alpha/Fe]}$.

	We identified candidate r-process enhanced stars by searching for deviations surrounding between the pseudo-continuum-normalised flux and the best-fitting model spectrum surrounding

	 flux and the pseudo-continuum-normalised spectra

	 with an over-abundance of Europium by searching for deviations from the normalized spectra supplied by \textit{The Cannon}. A negative deviation implies an enhancement in a particular element while a positive deviation implies a depletion (compared to what the data-driven model predicted).
